### 2018-03-28 latex/sc18/experiments.tex
synthetic and machine details included

\subsubsection{Real World}
\subsubsection{Synthetic}

\subsection{Machine Details}

>>>>

\subsubsection{Real World}

\subsubsection{Synthetic}
For the synthetic datasets, our open source code supports (a) low-rank tensor (b) uniform random and (c) positive shifted normal distribution of $\mathfrak{N}(3,1)$ -- that is change the mean such that all the random numbers are positive. We considered three different synthetic matrices for different cases. For baseline comparison with Liavas \cite{LKLHS18}, we considered a three mode 
uniform of size 1024x1024x1024 on processor grids $2^k \times 2^k \times 2^k$ for $k \in {0,1,2,3}$. We used the uniform five 
mode synthetic tensor with dimension $64\times 64\times 64\times 64\times 64$ on processor grids 
$1\times1\times1\times1\times1$, $2\times1\times1\times1\times1$, $\dots$, $2\times2\times2\times2\times2$ for strong scaling 
experiments.  In the case of weak scaling of four mode synthetic tensors with (D) and without (N) the use of dimension trees.  The 
tensor and processor grid dimensions are $128k\times 128k\times 128k\times 128k$ and $k\times k\times k\times k$ for $k\in\{1,2,3,4\}$. In all the cases the dimensions were considered such that synthetic tensors can be accomodated even on single node with 64GB for scale up plots.

\subsection{Machine Details}
The entire experimentation was performed on Eos -- a super computer in Oak Ridge Leadership Computing Facility (OLCF). 
Eos is a 736-node Cray® XC30? cluster with a total of 47.104TB of memory. Its processor is the Intel® Xeon® E5-2670. It features 
16 I/O service nodes and 2 external login nodes. Its compute nodes are organized in blades. Each blade contains 4 nodes and every node has 2 sockets with 8 physical cores and 64GB memory. Even though the machine support Intel's hyper-threading (HT), we restricted the total number of OpenMP threads to match the number of physical cores as HT offers minimal improvement for
 BLAS and LAPACK operations. In total, the Eos compute partition contains 11,776 traditional processor cores (23,552 logical cores 
 with HT Technology enabled) and some of the experiments peaked to 8,192 out of 11,776 physical cores that is approximately 
 70\% of the peak capacity.
